Electricity Usage in Toronto’s Public Facilities: Analyzing the Impact of Building Size on Energy Consumption

### 2024-09-24 paper/paper.qmd
change data name and code

Public infrastructure, including schools, libraries, healthcare centers, and government offices, forms the backbone of urban services in any modern city. As Toronto continues to expand, managing electricity usage in public buildings becomes increasingly critical. Energy efficiency in public facilities not only reduces operational costs but also contributes to environmental goals, such as carbon reduction and climate change mitigation \cite{droege2018urban}.

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

@@

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

@@

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

@@

@@

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

@@

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

Public infrastructure, including schools, libraries, healthcare centers, and government offices, forms the backbone of urban services in any modern city. As Toronto continues to expand, managing electricity usage in public buildings becomes increasingly critical. Energy efficiency in public facilities not only reduces operational costs but also contributes to environmental goals, such as carbon reduction and climate change mitigation[@droege2018urban].

One of the primary determinants of electricity consumption is building size, commonly measured as Gross Floor Area (GFA). Larger buildings tend to consume more energy for lighting, heating, cooling, and equipment operations, but this relationship is influenced by other factors such as building type, operational hours, and energy management systems [@hong2019occupant]. As such, it is crucial for policymakers to understand how building size and other factors influence electricity consumption in Toronto’s public facilities [@li2011managing].

Several studies have shown that energy efficiency measures in public buildings can lead to significant reductions in electricity consumption. For example, retrofitting large government buildings or healthcare facilities with modern energy management systems can reduce energy use, while smaller buildings like libraries and schools often exhibit lower per-square-meter energy consumption [@eto2012impact; @santamouris2016innovative].

This paper explores the relationship between Property GFA (m²) and electricity usage (kWh) in over 500 public facilities in Toronto. The study aims to identify patterns in electricity consumption and provide insights for optimizing energy use in Toronto's public sector.

@@

```{r}
#| label: fig-Area
#| fig-cap: Density Plot for Property Area in Toronto
#| echo: false

@@

@@

```{r}
#| label: none
#| fig-cap: Relationship between wing length and width
#| echo: false
#| message: false
#| warning: false

analysis_data <- read.csv("/Users/liuzilin/Desktop/Toronto_annual_energy_consumption/data/analysis_data/analysis_data.csv")

analysis_data |>
  ggplot(aes(x=log_Area)) +
  geom_histogram(aes(y= ..density..,fill = "pink")) +
  geom_density() +
  ggtitle("Density Plot for Property Area in Toronto")
```

@@

```

@@

```

@@

```

@@

```
